---
title: "Loading Tables from HTML, JSON, and XML"
author: "Alice Friedman"
date: "October 9, 2018"
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: vignette
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Setup
```{r, results="hide", message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(prettydoc)
library(rvest)
library(dplyr)
library(jsonlite)
library(RCurl)
library(XML)
remove(list=ls())
```

##HTML
First, store the raw HTML file as an R object using the ```read_html``` function.
```{r}
books.html <- read_html("https://raw.githubusercontent.com/aliceafriedman/DATA607_HW_WK7/master/books.html")
```

Then, parse the R object, ```html```, using the ```html_nodes``` function from the ```rvest``` library.
```{r}
books.html.table <- html_nodes(books.html, "table")
books.html.table <- html_table(books.html.table[1], fill = TRUE) %>% as.data.frame() %>% glimpse()
class(books.html.table)
books.html.table %>% 
  kable() %>% kable_styling(bootstrap_options = "responsive")
```

##JSON
First, read, the JSON obects into R using the ```jsonlite``` pakage. By setting the ```simplifyVector``` option to ```TRUE```, this will automatically create a data frame.

Unlike reading from HTML, this will also create a row number.
```{r}
books.json <- read_json("https://raw.githubusercontent.com/aliceafriedman/DATA607_HW_WK7/master/books.json",  simplifyVector = TRUE)
class(books.json)
books.json %>% glimpse()
books.json %>%  kable() %>% kable_styling(bootstrap_options = "responsive")
```


##XML

Use ```RCurl``` function ```getURL``` to download the XML file from the web, then use the ```xmlParse``` function to read the XML file.

```{r}
books.xml <- getURL("https://raw.githubusercontent.com/aliceafriedman/DATA607_HW_WK7/master/books.xml")
books.xml <- xmlParse(books.xml)
Title <- xpathSApply(books.xml, "//book/title", fun=xmlValue)
Year <- xpathSApply(books.xml, "//book/Year", fun=xmlValue)
Auth1.Last <- xpathSApply(books.xml, "//book/Auth1.Last", fun=xmlValue)
Auth2.Last <- xpathSApply(books.xml, "//book/Auth2.Last", fun=xmlValue)
Auth1.First <- xpathSApply(books.xml, "//book/Auth1.First", fun=xmlValue)
Auth2.First <- xpathSApply(books.xml, "//book/Auth2.First", fun=xmlValue)
Short.Description <- xpathSApply(books.xml, "//book/Short.Description", fun=xmlValue)
books.xml.df <- data.frame(Title, Year, Auth1.Last, Auth1.First, Auth2.Last, Auth2.First, Short.Description)
glimpse(books.xml.df)
books.xml.df %>% kable() %>% kable_styling(bootstrap_options = "responsive")
```

##Conclusion

Althought the kables look identical, the XML-to-R process generates a data frame where each column is saved as a factor. The HTML and JSON files generated a file that correctly identified character and numeric values.
  
  
